Capturing Policies for BYOD

### 2016-11-08 paper.tex
work work work

\documentclass{article}

@@

@@

\usepackage{listings}
\lstdefinelanguage{AppPAL}{%
  morekeywords={if,inf,says,where,true,false,with,is},
  otherkeywords={can-act-as,can-say},
  sensitive=true,
  morestring=[b]',
  literate={\ inf\ }{{$\infty$}}5
}[keywords,strings]
\newcommand{\listingsize}[0]{\footnotesize}
\lstset{%
  basicstyle=\ttfamily\listingsize,
  keywordstyle=\ttfamily\slshape\listingsize,
  stringstyle=\sffamily\listingsize,
  columns=flexible,
  mathescape,
  tabsize=2,
  showstringspaces=true,
  %numbers=left,
  frame=single,
  breaklines=true,
  numberstyle=\tiny\ttfamily\color{Gray},
  commentstyle=\ttfamily\color{Gray}
}
\newcommand{\code}[2][]{\lstinline[breaklines=true, #1]{#2}}

\usepackage{framed}
\newcommand{\todo}[1]{\marginpar{\begin{framed}\footnotesize\sffamily\raggedright #1\end{framed}}}

\newenvironment{policyrule}[1]{%
  \begin{framed}\footnotesize
      \noindent\textbf{\sffamily #1}:~\itshape%
}{%
  \end{framed}
}

\title{Capturing Policies for BYOD}
\author{Joseph Hallett and David Aspinall}
\begin{document}
\maketitle

\begin{abstract}
  % 4 Sentences
\end{abstract}

@@

\newcommand{\textbra}[1]{\ensuremath{\left\langle \text{\sffamily #1} \right\rangle}}
\begin{quote}
  Digital camera embedded on handheld devices \emph{might} be disabled in restricted environments, according to \textbra{COMPANY NAME} risk analysis.
  In sensitive facilities, information can be stolen using pictures and possibly sent using MMS or E-mail services.

  In high-security facilities such as R\&D labs or design manufacturers, camera MUST be disabled.
  Furthermore, MMS messages should be disabled as well, to prevent malicious users from sending proprietary pictures.
\end{quote}

@@

@@

@@

>>>>

\documentclass{easychair}

@@

\newcommand{\etal}{et~al.\@}

@@

\usepackage{listings}
\lstdefinelanguage{AppPAL}{%
  morekeywords={if,inf,says,where,true,false,with,is},
  otherkeywords={can-act-as,can-say},
  sensitive=true,
  morestring=[b]',
  literate={\ inf\ }{{$\infty$}}5
}[keywords,strings]
\newcommand{\listingsize}[0]{\footnotesize}
\lstset{%
  basicstyle=\normalfont\ttfamily\listingsize,
  keywordstyle=\normalfont\ttfamily\slshape\listingsize,
  stringstyle=\normalfont\sffamily\listingsize,
  columns=flexible,
  mathescape,
  tabsize=2,
  showstringspaces=true,
  %numbers=left,
  frame=single,
  breaklines=true,
  numberstyle=\tiny\ttfamily\color{Gray},
  commentstyle=\ttfamily\color{Gray}
}
\newcommand{\code}[2][]{\lstinline[breaklines=true, #1]{#2}}

\usepackage{mdframed}
\newcommand{\todo}[1]{\marginpar{\begin{mdframed}[userdefinedwidth=1cm]\tiny\sffamily\raggedright #1\end{mdframed}}}

\newenvironment{policyrule}[1]{%
  \begin{mdframed}\footnotesize
      \noindent\textbf{\sffamily #1}:~\itshape%
}{%
  \end{mdframed}
}

\title{Capturing Policies for BYOD}
\author{Joseph Hallett and David Aspinall}
\institute{University of Edinburgh}
\begin{document}
\maketitle

\begin{abstract}
  % 4 Sentences
  BYOD policies are informally specified using natural language.
  Various tools and \ac{MDM} solutions can implement parts of the policies, but there isn't a means to tie the written policy to its enforcement method.
  In this paper we show how AppPAL can be used to capture policies for BYOD.
  We identify common BYOD idioms and delegation structures.
\end{abstract}

@@

\newcommand{\textbra}[1]{\ensuremath{\left\langle \text{\sffamily #1} \right\rangle}}
\begin{policyrule}{SANS}
  Digital camera embedded on handheld devices \emph{might} be disabled in restricted environments, according to \textbra{COMPANY NAME} risk analysis.
  In sensitive facilities, information can be stolen using pictures and possibly sent using MMS or E-mail services.

  In high-security facilities such as R\&D labs or design manufacturers, camera MUST be disabled.
  Furthermore, MMS messages should be disabled as well, to prevent malicious users from sending proprietary pictures.
\end{policyrule}

@@

    User \texttt{mustAcknowledged}(Policy)      & \cmark                 & \cmark                  & \cmark              & \cmark            & \cmark
    & Requires the user to acknowledge a  policy.                                          \\

@@

\subsubsection{Acknowledgement}

All of the policies looked at require their subjects to be aware and acknowledge certain rules or policies, 
  or that the company may perform certain actions.
For example the NHS and HiMSS policies state that the company will wipe devices remotely to protect confidential information if the device is lost.
Alongside these rules both policies also state that if an employee has personal information on the device then this will be lost also.
The employee is required to be aware of this, and in the case of the HiMSS policy, agree to hold the company harmless for the loss.

\begin{center}
  \noindent
  %\begin{minipage}{0.49\linewidth}
    \begin{policyrule}{HiMSS}
      I agree to hold XYZ Health System harmless for any loss relating to the
      administration of PDA/Smartphone connectivity to XYZ Health System systems
      including, but not limited to, loss of personal information stored on a
      PDA/Smartphone due to data deletion done to protect sensitive information
      related to XYZ Health System, its patients, members or partners.
      \normalfont
      \begin{lstlisting}
'xyz-health-system' says 'user' mustAcknowledged('data-loss-policy').
      \end{lstlisting}
    \end{policyrule}
  %\end{minipage}
  %\begin{minipage}{0.49\linewidth}
    \begin{policyrule}{NHS}
      Individuals who have personal data of any kind stored on a corporately
      issued mobile device must be aware that in the event of loss of the device
      the above data wipe will include removal of all personal data.
      \normalfont
      \begin{lstlisting}
'nhs-trust' says Staff:S can-say
  S hasAcknowledged('data-loss-policy').
'nhs-trust' says Staff:S mustAcknowledged('data-loss-policy').
      \end{lstlisting}
    \end{policyrule}   
  %\end{minipage}
\end{center}

Both the SANS and the siren-company policies use acknowledgements to link to other sets of rules that employees should be aware of.
These policies aren't further specified, and in the case of an acceptable use policy may be hard to enforce automatically.

\begin{policyrule}{SANS}
  Users MUST agree to the email security/acceptable use policy and eventually to the eCommerce security policy.
  \begin{lstlisting}
'company' says Employee:U mustAcknowledged('email-security'). 
'company' says Employee:U mustAcknowledged('acceptable-use'). 
'company' says Employee:U mustAcknowledged('ecommerce-security').
  \end{lstlisting}
\end{policyrule}
\begin{policyrule}{Sirens}
  The employee is expected to use his or her devices in an ethical manner at all times and adhere to the company's acceptable use policy.
  \begin{lstlisting}
'department' says Employee:E mustAcknowledged('acceptable-use').
  \end{lstlisting}
\end{policyrule}

\todo{Provide a template for what kinds of policy should be implemented like this and template AppPAL.}

\subsection{Delegation and Roles within Policies}

AppPAL requires all assertions be made by an explicit speaker.
When translating the policies the author of the policy is generally used as the speaker of the rule (\autoref{tab:principals}),
  with the exception of the HiMSS policy that is written as a contract the user is agreeing to.
All the policies delegate also describe other entities that might also make assertions.
With AppPAL policies any speaker can delegate a decision to another speaker (with restrictions on re-delegation).
This might be to a user to acknowledge a policy, or it might be to other groups in the company who are responsible for certain decisions.

In all of the policies we looked at the majority of the decisions are made by three speakers: 
  the company, the IT-department, and the users or employees.
All of the policies also delegate to a user (apart from HiMSS where the user is the primary speaker).
The user is typically responsible for providing information, such as agreements to policies, reporting devices missing, and updating passcodes.

The Sirens, SANS and NHS policy each describe an IT-department who are delegated to make some decisions.
The HiMSS policy also describes an \emph{xyz-health-system}, who act similarly to an IT-department.
These decisions are more varied and can overlap with the responsibilities of the company.
In the NHS and SANS policies the IT department is responsible for maintaining lists of activated devices.
In the Sirens and SANS policies the IT department maintains a list of what is installable on a device or not.

\begin{table}\centering\footnotesize
  \begin{tabular}{l l}
    \toprule
    Policy      & Primary Speaker           \\
    \midrule
    {SANS}      & \emph{company}            \\
    {HiMSS}     & \emph{user}               \\
    {NHS}       & \emph{nhs-trust}          \\
    {Edinburgh} & \emph{records-management} \\
    {Sirens}    & \emph{department}         \\
    \bottomrule
  \end{tabular}
  \label{tab:principals}
  \caption{Principal Speakers from each of the policies examined.}
\end{table}

@@

Companies have very little visibility into how their policies are implemented.
Morrow notes that \emph{``particularly with the BYOD trend IT professionals don't know if anti-virus software is installed or if it it's current''}~\cite{morrow_byod_2012}.
Even when devices have means to implement policies correctly it is difficult to ensure devices are properly configured when they are not corporately owned~\cite{tokuyoshi_security_2013}.
Our work aims to address these problem directly: by using formal languages we can link the policy to the implementation.

Armando~\etal~developed BYODroid as a tool for enforcing BYOD policies through a secure marketplace~\cite{armando_enabling_2014}.
Their tool allows companies to distribute a secure app~store where through a combination of static and dynamic tools they can verify that apps follow fine-grained permission policies.
Their policies are low level, based on ConSpec~\cite{aktug_conspec_2008}, allowing checks based on the JVM state.
Using their tool they implemented parts of a policy relating to personal networks, and data management for the NATO Communications and Information Agency~\cite{armando_developing_2016}.
Their work shows how parts of a BYOD policy can be checked for and enforced using tools.
An AppPAL policy might use BYODroid to ensure that a parts of a policy are enforced (as well as other tools for other parts).
AppPAL makes explicit how the natural language policy is implemented and by which tools.

Costantino~\etal~created a role-based access control scheme for BYOD devices that allowed a company to verify the devices within their network and what servers and services they had access to~\cite{costantino_towards_2013}. The scheme relied on devices having a TPM however to ensure policy violations were reported.

Other work has looked at using app wrapping to enforce more general policies.
Tools, such as Dr.~Android and Mr.~Hyde~\cite{jeon_dr._2012} and Aurasium~\cite{xu_aurasium:_2012}, have suggested app wrapping as a possible way to enforce policies.
This has the advantage that the device's underlying OS needn't be modified as the apps can be modified at the source code level.
Many commercial \ac{MDM} solutions offer app-wrapping as a feature~\cite{_ibm_????,_app_????}, however app wrapping alone without additional analysis is insufficient to enforce policies effectively~\cite{hao_effectiveness_2013}.
